PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-12-10 qfenv_paper/qf_environment.tex
Intro draft
Significant changes to intro

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Galaxies, in their detailed properties, carry the imprints of their surroundings, with a strong dependence of the quiescent fraction of galaxies on their local environment (e.g. \citealt{hubble36a, oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see \citealt{blanton09a}).  The strength of this dependence is itself a strongly decreasing function of galaxy stellar mass; at the extreme, the lowest mass ($<10^{9}$ $M_\odot$) galaxies end their star formation only in dense regions, and never in isolation (\citealt{geha12a}). These effects vary with redshift at least in the densest clusters, as observed in the changing fraction of late-type spirals relative to the field found in studies of the morphology-density relation (\citealt{dressler84a, Fasano:2000aa, Smith:2005aa, desai07a}). Clearly understanding the properties of galaxies in the present-day universe requires a careful investigation of the role of environment, and how that role changes over time.

@@

Nevertheless, the evolution of the role of environment is a relatively subtle effect and must be interpreted on top of the changes in overall the galaxy population. For instance, the most dramatic change in galaxy properties during the past eight billion years has been the remarkable decline in the star-formation rate of galaxies in the Universe (\citealt{hopkins06a}). This decline appears dominated by decreases in the rates of star-formation of individual galaxies (\citealt{Noeske:2007aa}). There is evidence that a large fraction of the decline is associated with strongly infrared-emitting starbursts (\citealt{bell05a, magnelli09a}). As \cite{cooper08a} and others have pointed out, because the environmental dependence of total star-formation rates at fixed redshift is relatively small, environmentally effects are unlikely to cause the overall star-formation rate decline.

Furthermore, during this universal decline, the major classes of galaxies that have existed at $z \sim 1$ remain firmly in place since (\citealt{bundy06a, borch06a, taylor09a, Moustakas:2013aa}). Although these classes have remained roughly the same relative number during this time, detailed observations of the stellar mass function find detectable changes in the quiescent and star-forming galaxy populations. There is a significant decline in the number density of massive/luminous star-forming galaxies accompanied by an increase in the number density of quiescent galaxies (\citealt{Bell:2004aa, Blanton:2006aa, bundy06a,  borch06a, Moustakas:2013aa}). The evolution of these two populations suggest a build up of the quiescent population caused by the cessation of star formation for some star-forming galaxies over time.

Of the numerous mechanisms that have been proposed to explain this cessation, some suggest that star-formation is quenched due to internal processes such as supernovae or active galactic nuclei that suppresses cold gas accretion (CITECITE). Other models suggest that environment dependent external processes such as ram-pressure stripping (CITE), strangulation (CITE), or harassment (CITE) contribute to the cessation. While discrepancies persist between these theoretical models and observations, many of the environment dependent processes have found observational support (CITECITE) suggesting that environment may play a role in ceasing star-formation.

@@

%The most dramatic change in galaxy properties during the past eight billion years has been a remarkable decline in the star-formation rate of galaxies in the Universe (\citealt{hopkins06a}). This decline  appears dominated by decreases in the rates of star-formation of individual galaxies (\citealt{Noeske:2007aa}). There is evidence that a large fraction of the decline is associated with strongly infrared-emitting starbursts (\citealt{bell05a, magnelli09a}). The decline does not appear to be due to a complete cessation of star formation for a large fraction of the star-forming population, as reflected in observations of the stellar mass function of quiescent and star-forming galaxies (\citealt{Blanton:2006aa, bundy06a,   borch06a, Moustakas:2013aa}).  These findings leave little room for the participation of environmentally-driven cessation of star formation in the global census of star-formation.  As \cite{cooper08a} and others have pointed out, because the environmental dependence of total star-formation rates at fixed redshift is relatively small, environmentally effects are unlikely to cause the overall star-formation rate decline.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Galaxies, in their detailed properties, carry the imprints of their surroundings, with a strong dependence of the quiescent fraction of galaxies on their local environment (e.g. \citealt{hubble36a, oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see \citealt{blanton09a}).  The strength of this dependence is itself a strongly decreasing function of galaxy stellar mass; at the extreme, the lowest mass ($<10^{9}$ $M_\odot$) galaxies end their star formation only in dense regions, and never in isolation (\citealt{geha12a}). These effects also vary with redshift at least in the densest clusters, as observed in the changing fraction of late-type spirals relative to the field, found in studies of the morphology-density relation (\citealt{dressler84a, Fasano:2000aa, Smith:2005aa, desai07a}). Clearly understanding the properties of galaxies in the present-day universe requires a careful investigation of the role of environment, and how that role changes over time.

@@

Nevertheless, the evolution of the role of environment is a relatively subtle effect and must be interpreted within the context of the evolving galaxy population. For instance, the most dramatic change in galaxy properties during the past eight billion years has been the remarkable decline in the star-formation rate of galaxies in the Universe (\citealt{hopkins06a}). This decline appears dominated by decreases in the rates of star-formation of individual galaxies (\citealt{Noeske:2007aa}). There is evidence that a large fraction of the decline is associated with strongly infrared-emitting starbursts (\citealt{bell05a, magnelli09a}). As \cite{cooper08a} and others have pointed out, because the environmental dependence of total star-formation rates at fixed redshift is relatively small, environmental effects are unlikely to cause the overall star-formation rate decline.

During this period, the major classes of galaxies that we observe today have already been firmly in place (\citealt{bundy06a, borch06a, taylor09a, Moustakas:2013aa}). Though not as dramatic as the history of galaxies prior to $z \sim 1$, detailed observations of the stellar mass function find significant evolution of the quiescent and star-forming galaxy populations. Since $z \sim 1$, the significant decline in the number density of massive/luminous star-forming galaxies is accompanied by an increase in the number density of quiescent galaxies  (\citealt{Blanton:2006aa, bundy06a,  borch06a, Moustakas:2013aa}). On the color-magnitude diagram, this corresponds to the doubling of the red sequence over this period (\citealt{Bell:2004aa, borch06a, Faber:2007aa}). The correspondence of these changes in the galaxy population suggest the existence of a mechanism that causes the cessation of star-formation in star-forming galaxies.

Of the numerous mechanisms that have been proposed to explain this cessation, favored models suggest that internal processes such as supernovae or active galactic nuclei heat the gas within the galaxy, which consequently suppress the cold gas supply used for star-formation (\citealt{Keres:2005aa, Croton:2006aa, Dekel:2008aa}). Other models propose that environment dependent external processes such as ram-pressure stripping (\citealt{Gunn:1972aa, Bekki:2009aa}), strangulation (\citealt{Larson:1980aa, Balogh:2000aa}), or harassment (\citealt{Moore:1998aa}) contribute to the cessation. Many of these proposed processes have received observational support. \cite{Weinmann:2006aa} and \cite{Peng:2010aa}, for example, credit internal processes for quenching star-formation, especially in massive galaxies. Similarly, a number of observations support the existence of environment dependent external processes (\citealt{Iovino:2010aa, geha12a, Kovac:2014aa}). \cite{Peng:2010aa} and others further argue that internal and external processes both contribute to the cessation of star-formation with internal processes more dominant in massive galaxies and external processes dominating the less massive regime. While discrepancies persist between theoretical models and observations, a large number of observations suggest that environment plays a significant role in ceasing star-formation.

@@

%The most dramatic change in galaxy properties during the past eight billion years has been a remarkable decline in the star-formation rate of galaxies in the Universe (\citealt{hopkins06a}). This decline  appears dominated by decreases in the rates of star-formation of individual galaxi es (\citealt{Noeske:2007aa}). There is evidence that a large fraction of the decline is associated with strongly infrared-emitting starbursts (\citealt{bell05a, magnelli09a}). The decline does not appear to be due to a complete cessation of star formation for a large fraction of the star-forming population, as reflected in observations of the stellar mass function of quiescent and star-forming galaxies (\citealt{Blanton:2006aa, bundy06a,   borch06a, Moustakas:2013aa}).  These findings leave little room for the participation of environmentally-driven cessation of star formation in the global census of star-formation.  As \cite{cooper08a} and others have pointed out, because the environmental dependence of total star-formation rates at fixed redshift is relatively small, environmentally effects are unlikely to cause the overall star-formation rate decline.
